### 2021-07-01 README.Rmd
adding DOI to readme

This repo contains code and data needed to reproduce "Assessing the Population-level Conservation Effects of Marine Protected Areas" by Ovando et al. In Prep.

>>>>

This respository contains code and data needed to reproduce "Assessing the Population-level Conservation Effects of Marine Protected Areas" by Ovando et al. 2021. The manuscript in *Conservation Biology* can be accessed at https://conbio.onlinelibrary.wiley.com/doi/10.1111/cobi.13782

## Abstract

## Reproducing Results
